Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems

### 2024-06-19 final/oup-authoring-template.tex
Add Sheriff changes

\author[1,2]{Mauro Silberberg\ORCID{0000-0002-2402-1100}}
\author[3]{Henning Hermjakob\ORCID{0000-0001-8479-0262}}
\author[3]{Rahuman S. Malik-Sheriff\ORCID{0000-0003-0705-9809}}
\author[1,2,$\ast$]{Hernán E. Grecco\ORCID{0000-0002-1165-4320}}

@@

\address[1]{\orgname{Universidad de Buenos Aires, Facultad de Ciencias Exactas y Naturales, Departamento de Física}, \orgaddress{\state{Buenos Aires}, \country{Argentina}}}
\address[2]{\orgname{CONICET - Universidad de Buenos Aires, Instituto de Física de Buenos Aires (IFIBA)}, \orgaddress{\state{Buenos Aires}, \country{Argentina}}}
\address[3]{\orgdiv{European Bioinformatics Institute}, \orgname{European Molecular Biology Laboratory (EMBL-EBI)}, \orgaddress{\street{Wellcome Genome Campus}, \state{Cambridge}, \country{UK}}}

@@

\section{Acknowledgments}
The authors thank the anonymous reviewers for their valuable suggestions.
This work was supported in part by funds from
the Agencia I+D+i (PICT-2018-01516),
and Universidad de Buenos Aires (UBAINT Doctoral, REREC-2023-593-E-UBA-REC).

>>>>

\author[1,2,3]{Mauro Silberberg\ORCID{0000-0002-2402-1100}}
\author[3]{Henning Hermjakob\ORCID{0000-0001-8479-0262}}
\author[3,4]{Rahuman S. Malik-Sheriff\ORCID{0000-0003-0705-9809}}
\author[1,2,$\ast$]{Hernán E. Grecco\ORCID{0000-0002-1165-4320}}

@@

\address[1]{
  \orgname{Universidad de Buenos Aires, Facultad de Ciencias Exactas y Naturales, Departamento de Física},
  \orgaddress{\state{Buenos Aires}, \country{Argentina}}
}
\address[2]{
  \orgname{CONICET - Universidad de Buenos Aires, Instituto de Física de Buenos Aires (IFIBA)},
  \orgaddress{\state{Buenos Aires}, \country{Argentina}}
}
\address[3]{
  \orgdiv{European Bioinformatics Institute},
  \orgname{European Molecular Biology Laboratory (EMBL-EBI)},
  \orgaddress{\street{Wellcome Genome Campus}, \state{Cambridge}, \country{UK}}
}
\address[4]{
  Secondary Affiliation:
  \orgdiv{Department of Surgery and Cancer, Faculty of Medicine},
  \orgname{Imperial College London},
  \orgaddress{\state{London}, \country{UK}}
}

@@

\section{Acknowledgments}
This work was supported in part by funds from
the Agencia I+D+i (PICT-2018-01516),
Universidad de Buenos Aires (UBAINT Doctoral, REREC-2023-593-E-UBA-REC),
and EMBL core funding.
